---
title: "poc"
author: "smd"
date: "`r Sys.Date()`"
output: html_document
---



Setup
```{r}
setwd("~/GitHub/csv_scd2")
library(tidyverse)
library(janitor)
library(logger)
library(digest)

# makes log text colourful
log_layout(layout_glue_colors)
```

pulling in dummy data to test with 
```{r}
extract1 <- read_csv("test1.csv", col_types = cols(.default = "c")) %>% 
  clean_names()

extract2 <- read_csv("test2.csv", col_types = cols(.default = "c")) %>% 
  clean_names()
```
 
hashing function to facilitate easy comparisons 
```{r}


hash_kv <- function(df_in, key_cols) {
  all_cols <- df_in %>%  colnames()
  value_cols <- setdiff(all_cols, key_cols)
  
  if (length(all_cols) == length(value_cols)) {
    log_fatal("The key columns do not exist in the table!")
  } else {
    df_out <- df_in %>% 
      unite("key_combined", all_of(key_cols), sep = "|", remove = FALSE) %>% 
      mutate(key_hash = sapply(key_combined, digest, algo = "sha256")) %>% 
      unite("value_combined", all_of(value_cols), sep = "|", remove = FALSE) %>%
      mutate(value_hash = sapply(value_combined, digest, algo = "sha256")) %>% 
      select(-c(key_combined, value_combined))
  
    return(df_out)
  }  
  
}

```


building test historic and load tables
```{r}
keys <- c("name")

df_historic <- hash_kv(extract1, keys)

df_load <- hash_kv(extract2, keys) 

df_all <- bind_rows(df_historic, df_load) %>% 
  distinct()

kv_historic <- df_historic %>% 
  select(key_hash, value_hash) %>% 
  mutate(effective_date = ymd("1111/01/01")) %>% 
  mutate(expiry_date = ymd("9999/12/31"))

kv_load <- df_load %>% 
  select(key_hash, value_hash) %>% 
  mutate(load_date = ymd("2222/01/01"))
  

```
TO DO: need something to check that both the load and historic tables have the correct cols


```{r}
kv_historic %>% 
  group_by(key_hash) %>%
  summarize(
    n = n(), 
    .groups = "drop"
  ) %>% 
  filter(n > 1) %>% 
  nrow()
  
```




finding all new records in load table
```{r}
kv_new <- anti_join(kv_load, kv_historic, by = join_by(key_hash, value_hash))

```
TO DO: check to make sure that key only appears once in new_records; if not error out because I won't know which one to use


capping records in the historic table where the key has a new value in the load table
```{r}
kv_capped <- kv_new %>% 
  select(key_hash, load_date) %>% 
  left_join(kv_historic, ., by = join_by(key_hash)) %>% 
  mutate(expiry_date = if_else(is.na(load_date), expiry_date, load_date - days())) %>% 
  select(-load_date)
  
```

```{r}
df_out <- bind_rows(
    kv_capped,
    kv_new %>% 
      rename(effective_date = load_date) %>% 
      mutate(expiry_date = ymd("9999/12/31"))
  ) %>% 
  arrange(key_hash, effective_date) 




# %>% 
#   left_join(df_all, by = join_by(key_hash, value_hash))
  
```


```{r}
x <- read_csv("test_all.csv")
```

```{r}
x %>% 
  clean_names() %>% 
  arrange(name, join_date) %>% 
  View()
```

